Global search algorithms for one-dimensional multiextremal optimization problems with nonlinear constraints

### 2017-10-17 2017/ParOptBook/Chapter4.tex
Chapters 4 and 5 are updated

\title{Global search algorithms for one-dimensional multiextremal optimization problems with nonlinear constraints}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Name of First Author and Name of Second Author}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{Name of First Author \at Name, Address of Institute, \email{name@email.address}
\and Name of Second Author \at Name, Address of Institute \email{name@email.address}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

>>>>

\title{Global search algorithms for one-dimensional multiextremal optimization problems with nonlinear constraints}
\titlerunning{Global optimization with nonlinear constraints}

\author{Konstantin Barkalov, Victor Gergel, Roman Strongin}
\authorrunning{K. Barkalov, V.Gergel, R. Strongin}

\institute{Konstantin Barkalov,  Victor Gergel, Roman Strongin \at Lobachevsky State University of Nizhni Novgorod,  Nizhni Novgorod, Russia \email{konstantin.barkalov@itmm.unn.ru}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle
